A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828: supplementary material

### 2018-09-11 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

cities <- c(
	      "Lund",
	      "Other",
	      "Stockholm",
	      "Tartu",
	      "Turku",
	      "Uppsala",
	      "Vyborg",
	      "Gothenburg",
	      "Linköping",
	      "Greifswald"	      
	    )
city.colors <- stata_pal("s2color")(length(cities))
names(city.colors) <- cities

languages <- c(
	      "Finnish",
	      "Other",
	      "Swedish",
	      "French",
	      "German",
	      "Hebrew",
	      "Latin",
	      "Russian"
	    )
lang.colors <- stata_pal("s2color")(length(city.colors))
names(lang.colors) <- languages

@@

# Data with years limited as well
df.full.1911 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1911)
df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)

@@

df0 <- df.full
cols <- list(FNB = "blue", SNB = "darkred")
```

@@

```{r Figure_2, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
#theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(Catalogue, publication_decade) %>% tally()

brsy <- seq(0, 1e4, 2000)
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = Catalogue,
		    color = Catalogue)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Title count (n)") +
       xlab("Decade") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       scale_y_continuous(breaks = brsy, labels = brsy) +
       guides(
         shape = guide_legend(title = "Catalogue", reverse = TRUE),
         color = guide_legend(title = "Catalogue", reverse = TRUE)	 
       ) +
       #ggtitl("Title count") +
       # ggtitle("Figure 2") +              
       scale_color_stata()
print(p)
```

@@

  df2 <- subset(df00, Catalogue == catal) %>%
           group_by(publication_decade, gatherings) %>%
	   summarize(paper = sum(paper, na.rm = TRUE)/1e6, n = n())
  # Million sheets

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (million sheets)")
  # p <- p + ylim(c(0, max(na.omit(df00$paper))))

@@

  p <- p + 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "FNB", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, 6.8, 1), limits = c(0, 6.8))
         #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
	                    # label = scientific_10)

@@

top <- c("Turku", "Vaasa", "Vyborg")
df <- filter(df, !is.na(publication_place))
df$publication_place[!df$publication_place %in% top] <- "Other"
top <- c(top, "Other")
df <- df %>%	
        #filter(publication_place %in% top) %>%	
        select(publication_decade, publication_place)
df.fennica <- df

npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
npub.fennica <- npub

@@

npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
npub.kungliga <- npub

@@

# Order by total publishing activity
npub$publication_place <- factor(npub$publication_place, levels = (npub %>%
                            group_by(publication_place) %>%
			    summarise(total = sum(n)) %>
			    % arrange(desc(total)))$publication_place)
npub <- npub %>% arrange(publication_place)
npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))

@@

@@

minyear <- 1640
maxyear <- 1828

@@

# Add title count per capita
dfm <- dfm %>% mutate(titles_per_capita = n/population)

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       #scale_color_stata() +
       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       #ggtitle("Title count per capita") +
       # ggtitle("Figure 11") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

#kable(dfm)
```

@@

```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE}
minyear <- 1640
maxyear <- 1828

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
#df$publication_place <- factor(df$publication_place, levels = levels(df0$publication_place))

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       # ggtitle("Figure 12") +              
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place"))

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Decade") +
       ylab("Title length (words)") +
       #ggtitle("Average title length") +
       # ggtitle("Figure 14") +                            
       #scale_fill_stata() +
       scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

  dfss <- subset(dff, publication_place == myplace)
  brs <- seq(min(dfss$publication_decade), max(dfss$publication_decade), 10)

@@

      p <- p + labs(subtitle = paste(myplace, "/", Catalogue)) +                 
      #scale_fill_stata() +
      scale_fill_manual(values = lang.colors[as.character(levels(dfss$language))]) +      
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
    pics[[paste(Catalogue, myplace, sep = "-")]] <- p
  }
}

#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))

@@

```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
Catalogue <- "FNB"
df <- filter(df0, Catalogue == "FNB") %>%
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
  select(publication_decade, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

brs <- seq(min(decade(df$publication_decade)), max(decade(df$publication_decade)), 10)

p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +
       #scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +
       # geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +             
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Subject topics (n)") +
       xlab("Decade") 
       # ggtitle("Figure 16")
       #ggtitle(paste("Topic richness (", Catalogue, ")", sep = ""))

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
       scale_y_continuous(label = scientific_10) + 
       #scale_color_stata() +
       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) 
       # ggtitle("Figure 17")
       #ggtitle(paste("Temporary sermons (", Catalogue, ")", sep = ""))
  print(p)
```

@@

# PAPER CONSUMPTION
#theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) 
       # ggtitle("Figure 18")       
       # ggtitle(paste("Devotional literature (", Catalogue, ")", sep = ""))

#print(p + theme_light(scalingfactor))
print(p)
```

>>>>

cities <- c(
	      "Lund",
	      "Other",
	      "Stockholm",
	      "Tartu",
	      "Turku",
	      "Uppsala",
	      "Vyborg",
	      "Gothenburg",
	      "Linköping",
	      "Greifswald"	      
	    )
city.colors <- stata_pal("s2color")(length(cities))
names(city.colors) <- cities
city.colors[["Other"]] <- "#696969"

languages <- c(
	      "Finnish",
	      "Other",
	      "Swedish",
	      "French",
	      "German",
	      "Hebrew",
	      "Latin",
	      "Russian"
	    )
lang.colors <- stata_pal("s2color")(length(city.colors))
names(lang.colors) <- languages
lang.colors[["Other"]] <- "#696969"
#lang.colors[["Hebrew"]] <- "#55752f"
#lang.colors[["Swedish"]] <- "#c10534"

@@

@@

# Data with years limited as well
df.full.1911 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1911)
df0 <- df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
cols <- list(FNB = "blue", SNB = "darkred")
```

@@

```{r Figure_2, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
df <- df0 %>% group_by(Catalogue, publication_decade) %>% tally()

brsy <- seq(0, 1e4, 2000)
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = Catalogue,
		    color = Catalogue)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Title count (n)") +
       xlab("Decade") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       scale_y_continuous(breaks = brsy, labels = brsy) +
       guides(
         shape = guide_legend(title = "Catalogue", reverse = TRUE),
         color = guide_legend(title = "Catalogue", reverse = TRUE)	 
       ) +
       scale_color_stata()
print(p)
```

@@

  df2 <- subset(df00, Catalogue == catal) %>%
           group_by(publication_decade, gatherings) %>%
	   summarize(paper = sum(paper, na.rm = TRUE), n = n())
  # Million sheets

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")

@@

  p <- p + 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "FNB", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, 6.8, 1)*1e6, limits = c(0, 6.8)*1e6,
	                    label = scientific_10)
         #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
	                    # label = scientific_10)

@@

top <- c("Turku", "Vaasa", "Vyborg")
df <- filter(df, !is.na(publication_place))
df$publication_place[!df$publication_place %in% top] <- "Other"
top <- c(top, "Other")
df <- df %>% select(publication_decade, publication_place)
df.fennica <- df

npub <- df %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
npub.fennica <- npub

@@

npub <- df %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
npub.kungliga <- npub

@@

# Order by total publishing activity
npub$publication_place <- factor(npub$publication_place, levels = (npub %>%
                            group_by(publication_place) %>%
			    summarise(total = sum(n)) %>%
			    arrange(desc(total)))$publication_place)
npub <- npub %>% arrange(publication_place)
npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))

@@

npub$publication_place <- factor(npub$publication_place, levels = rev(c("Other", setdiff(npub$publication_place, "Other"))))

@@

@@

# Add title count per capita
dfm <- dfm %>% mutate(titles_per_capita = n/population)
dfm$publication_place <- gsub("Linkoping", "Linköping", dfm$publication_place)

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
       scale_x_continuous(breaks = brs, labels = labs) +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)
```

@@

```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE}
# Take cities from SNB except Turku
cat <- "SNB"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	      filter(Catalogue == cat) %>%
              filter(publication_decade %in% pop$publication_decade) %>%
	      select(publication_decade, publication_place) %>%	      
	      group_by(publication_decade, publication_place) %>%
	      summarise(n = n())

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place"))

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Decade") +
       ylab("Title length (words)") +
       scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

  dfss <- subset(dff, publication_place == myplace)
  brs <- seq(min(df.full$publication_decade), max(df.full$publication_decade), 10)

@@

      p <- p + labs(subtitle = paste(myplace, "/", Catalogue)) +                 
      scale_fill_manual(values = lang.colors[as.character(levels(dfss$language))]) +      
      scale_x_continuous(breaks = brs,
                         labels = insert_minor(brs, 5),
                         limits = c(min.year, max.year)) +  
      guides(fill = guide_legend(title = "")) 
    pics[[paste(Catalogue, myplace, sep = "-")]] <- p
  }
}

@@

```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
Catalogue <- "FNB"
df <- filter(df0, Catalogue == "FNB") %>%
  select(publication_decade, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

brs <- seq(min(decade(df$publication_decade)), max(decade(df$publication_decade)), 10)
p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +             
       scale_x_continuous(breaks = brs,
                          labels = insert_minor(brs, 2,
			  start = century(min(brs)) + 40)) +                 
       ylab("Topical terms (n)") +
       xlab("Decade")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = 1600)) +
       scale_y_continuous(label = scientific_10) + 
       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) 
  print(p)
```

@@

# PAPER CONSUMPTION
#theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10)

### 2018-09-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
ok

fen <- subset(df0, catalog == "FNB")
kun <- subset(df0, catalog == "SNB")
cats <- list(FNB = fen, SNB = kun)

@@

for (cat in unique(df0$catalog)) {

  dd <- subset(df0, catalog == cat)[, selected.fields]

@@

 * FNB: ```r nrow(subset(df0, catalog == "FNB"))```
 * SNB: ```r nrow(subset(df0, catalog == "SNB"))```

@@

```{r author, echo=FALSE, message=FALSE, warning=FALSE}
field <- "author"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
knitr::kable(df, digits = 1, format = "markdown")
```

@@

In FNB, we have identified ```r sum(subset(df0, catalog == "FNB")$multilingual)``` multilingual documents in the investigated time period. In SNB, the multilingual documents have not been analyzed yet. We use the primary language of the document for summaries.

@@

```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
field <- "language_primary"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
colnames(df) <- gsub("language", "Language", colnames(df))
knitr::kable(df, format = "markdown")
```

@@

Proportion (%) of gatherings in the FNB and SNB catalogues. The gatherings with a prevalence less than 1% in both catalogues have been combined into the "Other" category.

```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
df <- df0 %>% group_by(catalog, gatherings) %>%
              summarise(n = n())
df <- spread(df, catalog, n, fill = 0)
colnames(df) <- c("Gatherings", "FNB", "SNB")
df$Gatherings <- as.character(df$Gatherings)
df$Gatherings <- gsub("NA", "Missing", df$Gatherings)

@@

p <- ggplot(df) +
       geom_histogram(aes(x = pagecount,
		    group = gatherings,       
                    #y = ..count../sum(..count..),
                    fill = gatherings),
                    color = "black",
		    alpha = 0.5
		    ) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +
       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
       scale_fill_manual(values = unname(cols)) +       
       facet_grid(catalog ~ gatherings) +
       guides(fill = "none") + 
       labs(y = "Frequency (n)") +
       theme(axis.text = element_text(size=12))
print(p)
```

@@

df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
knitr::kable(df, format = "markdown")
```

@@

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, figh.height=4, out.width = "300px"}
theme_set(theme_bw(20))
df <- df0
names(df) <- gsub("catalog", "Catalog", names(df))
df <- df %>% group_by(Catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, fill = Catalog)) +
       geom_bar(color = "black",
         position = "dodge", stat = "identity") +
       guides(fill = guide_legend(reverse = TRUE)) +
       labs(x = "Publication decade",
            y = "Frequency (n)") +
       scale_fill_manual(values = rev(c("darkgray", "black"))) #+
       #theme(axis.text = element_text(size=15))
print(p)
```

@@

In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$publisher))``` unique publishers, and ```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$publisher), na.rm = TRUE))```% of the documents have publisher information. We have not analyzed publishers in SNB, where the availability of harmonized publisher information is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$publisher), na.rm = TRUE))```%).

@@

We use here the term "Topic" for the "Topical term" MARC field 650a for brevity. In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$Topic))``` unique topics. ```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$Topic), na.rm = TRUE))```% of the documents have topic information. We have not analyzed topics in SNB, where the availability of harmonized topics is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$Topic), na.rm = TRUE))```%).

>>>>

fen <- subset(df0, Catalogue == "FNB")
kun <- subset(df0, Catalogue == "SNB")
cats <- list(FNB = fen, SNB = kun)

@@

for (cat in unique(df0$Catalogue)) {

  dd <- subset(df0, Catalogue == cat)[, selected.fields]

@@

 * FNB: ```r nrow(subset(df0, Catalogue == "FNB"))```
 * SNB: ```r nrow(subset(df0, Catalogue == "SNB"))```

@@

```{r author, echo=FALSE, message=FALSE, warning=FALSE}
field <- "author"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(Catalogue) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
knitr::kable(df, digits = 1, format = "markdown")
```

@@

In FNB, we have identified ```r sum(subset(df0, Catalogue == "FNB")$multilingual)``` multilingual documents in the investigated time period. In SNB, the multilingual documents have not been analyzed yet. We use the primary language of the document for summaries.

@@

```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
field <- "language_primary"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(Catalogue) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
colnames(df) <- gsub("language", "Language", colnames(df))
knitr::kable(df, format = "markdown")
```

@@

Proportion (%) of gatherings in the FNB and SNB Catalogues. The gatherings with a prevalence less than 1% in both Catalogues have been combined into the "Other" category.

```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
df <- df0 %>% group_by(Catalogue, gatherings) %>%
              summarise(n = n())
df <- spread(df, Catalogue, n, fill = 0)
colnames(df) <- c("Gatherings", "FNB", "SNB")
df$Gatherings <- as.character(df$Gatherings)
df$Gatherings <- gsub("NA", "Missing", df$Gatherings)

@@

p <- ggplot(df) +
       geom_histogram(aes(x = pagecount,
		    group = gatherings,       
                    #y = ..count../sum(..count..),
                    fill = gatherings),
                    color = "black",
		    alpha = 0.5
		    ) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +
       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
       scale_fill_manual(values = unname(cols)) +       
       facet_grid(Catalogue ~ gatherings) +
       guides(fill = "none") + 
       labs(y = "Frequency (n)") +
       theme(axis.text = element_text(size=12))
print(p)
```

@@

df <- df %>% group_by(Catalogue) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
knitr::kable(df, format = "markdown")
```

@@

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, figh.height=4, out.width = "300px"}
theme_set(theme_bw(20))
df <- df0
names(df) <- gsub("Catalogue", "Catalogue", names(df))
df <- df %>% group_by(Catalogue, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, fill = Catalogue)) +
       geom_bar(color = "black",
         position = "dodge", stat = "identity") +
       guides(fill = guide_legend(reverse = TRUE)) +
       labs(x = "Publication decade",
            y = "Frequency (n)") +
       scale_fill_manual(values = rev(c("darkgray", "black"))) #+
       #theme(axis.text = element_text(size=15))
print(p)
```

@@

In FNB, the data includes ```r  length(unique(subset(df0, Catalogue == "FNB")$publisher))``` unique publishers, and ```r  round(100 * mean(!is.na(subset(df0, Catalogue == "FNB")$publisher), na.rm = TRUE))```% of the documents have publisher information. We have not analyzed publishers in SNB, where the availability of harmonized publisher information is currently low (```r  round(100 * mean(!is.na(subset(df0, Catalogue == "SNB")$publisher), na.rm = TRUE))```%).

@@

We use here the term "Topic" for the "Topical term" MARC field 650a for brevity. In FNB, the data includes ```r  length(unique(subset(df0, Catalogue == "FNB")$Topic))``` unique topics. ```r  round(100 * mean(!is.na(subset(df0, Catalogue == "FNB")$Topic), na.rm = TRUE))```% of the documents have topic information. We have not analyzed topics in SNB, where the availability of harmonized topics is currently low (```r  round(100 * mean(!is.na(subset(df0, Catalogue == "SNB")$Topic), na.rm = TRUE))```%).
